---
title: "TRACE and INEXDA"
author: 
  - "Lars Vilhuber"
date:  2025-06-18
---

```{r config,include=FALSE}
library(readr)
library(here)
library(knitr)
library(dplyr)
library(ggplot2)
library(qualtRics)
library(lubridate)
library(qrcode)

# qualtRics secrets are read from the environment:
# - QUALTRICS_API_KEY
# - QUALTRICS_BASE_URL
# Let's check that they are there:

message(Sys.getenv("QUALTRICS_BASE_URL"))

# The repository name

message(Sys.getenv("GITHUB_REPOSITORY"))

# Process the repository name to generate the URL
# - split the two components
# - combine them into a URL with 'github.io' in the middle

GITHUB_REPOSITORY <- Sys.getenv("GITHUB_REPOSITORY")
GITHUB_REPOSITORY_PARTS <- strsplit(GITHUB_REPOSITORY, "/")[[1]]
REPOSITORY_URL <- paste0("https://github.com/", GITHUB_REPOSITORY)
WEBSITE_URL <- paste0("https://", GITHUB_REPOSITORY_PARTS[1], ".github.io/", GITHUB_REPOSITORY_PARTS[2])

# Qualtrics data for Day 1:
# you can find this with all_surveys() %>% arrange(creationDate) %>% head()

QUALTRICS_FULL_URL <- "https://illinois.qualtrics.com/jfe/form"

# Public Qualtrics URL for day 2

QUALTRICS_DAY2 <- "SV_6lZpBNiXsq1pDXo"

# Qualtrics confidential

QUALTRICS_DASHBOARD <- "https://cornell.yul1.qualtrics.com/Q/MyProjectsSection"

# Time when this was posted (discard anything before that)

QUALTRICS_DAY2_STIME <- ymd_hms("2025-06-17 23:59:00")
QUALTRICS_DAY2_ETIME <- ymd_hms("2025-06-19 23:59:00")

if (!dir.exists(here::here("data"))) {
  dir.create(here::here("data"))
}
```

::: {.panel-tabset}

## Follow along

```{r qrcode}
#| echo: false

code <- qr_code(WEBSITE_URL)
plot(code)

```


## What is TRACE?

- <https://transparency-certified.github.io/>
  - [Personas](https://transparency-certified.github.io/trace-specification/docs/users.html)
  - [Barriers to transparency](https://transparency-certified.github.io/trace-specification/docs/barriers.html)
  - [TRACE Elements: TRO and TRS](https://transparency-certified.github.io/trace-specification/docs/elements.html)
- [A sample implementation - walkthrough](https://transparency-certified.github.io/trace-specification/docs/sample-implementation.html)


## Close...

- [cascad](https://www.cascad.tech/)
  - [The Role of Third-Party Verification in Research Reproducibility](https://doi.org/10.1162/99608f92.6d4bf9eb)
- [IAB FDZ](https://fdz.iab.de/en/data-access/on-site-use/)
- [World Bank](https://reproducibility.worldbank.org/)
  - [Introducing Reproducible Research Standards at the World Bank](https://doi.org/10.1162/99608f92.21328ce3)
  - [Example report 1](https://reproducibility.worldbank.org/index.php/catalog/288/study-description)
  - [Example report 2](https://reproducibility.worldbank.org/index.php/catalog/224/related-materials)


## Survey 

You have work to do!

<`r file.path(QUALTRICS_FULL_URL,QUALTRICS_DAY2)`>

### Results

```{r downloaddata2,include=FALSE,eval=FALSE}
# download data to local location

data2.raw <- fetch_survey(surveyID = QUALTRICS_DAY2, verbose = TRUE) 
data2 <- data2.raw |>
        filter(Status != "Survey Preview") |>
        filter(Consent == "I agree that my data will be used in the manner described.") |>
        filter(StartDate > QUALTRICS_DAY2_STIME & EndDate < QUALTRICS_DAY2_ETIME) |>
  # renaming variables
  select(StartDate,EndDate,Status,Finished,RecordedDate,ResponseId,Consent,Preferred_topic,Degree,JEL_primary,
         starts_with("JEL_secondary"),starts_with("Versioning_"))


```

```{r create_table2, results='asis', include=TRUE,eval=FALSE,echo=FALSE,message=FALSE}

if ( nrow(data2) >0 ) {
data2 |>
  select(Preferred_topic) |>
  group_by(Preferred_topic) |>
  summarise(Frequency=n()) |>
  ungroup() |>
  mutate(Percent = round(Frequency/nrow(data2)*100,2)) -> data2.table

data2.table |> kable()
} else {
  cat("No data yet. Check back later.")
}
```

- 🔒[Alt link](`r QUALTRICS_DASHBOARD`)

### Notes

```{r, child=c(here::here('notes.md'))}
```

:::

